\documentclass{resume} % The style class
\usepackage[bottom=0.55in,right=0.55in,left=0.55in, top=0.55in]{geometry}
\usepackage{hyperref}
\usepackage{enumitem}
\name{Aaron Steinberg}

\address{aaron@aa.codes $\mid$ \href{https://aa.codes}{https://aa.codes} $\mid$ \href{https://github.com/azsteinb}{https://github.com/azsteinb}}

%\address{\href{https://aa.codes}{https://aa.codes}}

\begin{document}

\begin{rSection}{Education}
    \textbf{University of California, Santa Cruz}
    \\ Baskin School of Engineering
    \\ Bachelor of Science, Computer Science
    \hfill{\textbf {Sep. 2019 - Jun. 2023}}
\end{rSection}

\begin{rSection}{Work Experience}
    {\textbf{Security Software Engineer}} @ \textit{{Aurora Innovation}}
    \hfill{\textbf {Mar. 2024 - Present}}
    \\{\textbf{Contracting Security Software Engineer}} @ \textit{{Aurora Innovation}}
    \hfill{\textbf {Sep. 2023 - Mar. 2024}}
    \vspace{-0.65em}
    \begin{itemize}[noitemsep]
        \item Developed and maintained security infrastructure for autonomous vehicle systems, both on the vehicle and in the cloud
        \item Designed, implemented, and scaled secure container signing, deployment and verification systems
        \item Designed and implemented a role based access control (RBAC) system for cloud resources
        \item Developed and maintained secure boot, secure update, key management, and device identity systems for proprietary embedded hardware
        \item C, C++, Golang, Python, Bazel, AWS, gRPC, Kubernetes, HashiCorp Vault, Terraform, Spacelift
    \end{itemize}

    {\textbf{Consulting Software Engineer} @ \textit{OrganizeMyPeople}}
    \hfill{\textbf {Apr. 2023 - Sep. 2023}}
    \vspace{-0.65em}
    \begin{itemize}[noitemsep]
        \item Created an art studio booking and billing system for a non-profit art center
        \item Maintianed CRMs and databases for a variety of non-profit organizations
        \item PHP, Javascript, Laravel, React, Microsoft SQL Server
    \end{itemize}

    {\textbf{Google Workspace Subject Matter Expert} @ \textit{UCSC ITS} }
    \hfill{\textbf {Dec. 2021 - Jul. 2023}}
    \vspace{-0.65em}
    \begin{itemize}[noitemsep]
        \item Provided technical support to students and internal ITS teams on Google Workspace applications and services
        \item Created Python scripts for auditing resource usage and automating administrative tasks
    \end{itemize}

    {\textbf{Computer Systems and C Programming Grader} @ \textit{UCSC} }
    \hfill{\textbf {Mar. 2021 - Jun. 2021}}

    {\textbf{Help Desk Technician} @ \textit{UCSC ITS}}
    \hfill{\textbf {Dec. 2020 - Dec. 2021}}
    
    {\textbf{Bioinformatics Software Engineer Intern} @ \textit{Progenabiome}}
    \hfill{\textbf {Jun. 2019 - Sept. 2019}}

\end{rSection}

\begin{rSection}{Projects and Papers}

    {\textbf{Bflock:}} A C library for safer \& easier multithreaded IO operations.
    
    {\textbf{Locally Imagined:}} An online art market place specialized to Santa Cruz, CA.
    \\ Tech used: Golang, GOA, React, Heroku, Amazon S3, \& Postgresql.
    
    {\textbf{MediBill:}} Medical Bill Analyzer, CruzHacks 2022 First Place Winner.
    \\Tech used: Javascript, Python, Vue.js, Google Cloud Functions.

    {\textbf{A Brief Survey of Data Placement in a Geo-Distributed Storage System using ML}: Graduate distributed systems survey paper that explores ML-based data placement} 

    {\textbf{Reverse Proxy HTTP Load Balancer:} } Multithreaded, logging, and cache enabled. Written in C.
\end{rSection}

\begin{rSection}{Skills}
    {\textbf{Programming Languages:} } C, C++, Golang, Javascript, PHP, Python, SQL
    \\{\textbf{Technologies and Other Skills:} }
    Bazel, Buildkite, Cryptography, Distributed Systems, Embedded Systems, Git, gRPC, HashiCorp Vault, Key Management, Kubernetes, Laravel, LaTeX, Linux, Make, Measured Boot \& Device State Attestation, Metrics, Node, Operating Systems, Protocol Buffers, RBAC, React, Secure Boot, Spacelift, SSL/TLS, Terraform, Trace 32
\end{rSection}
    

\end{document}