\documentclass{resume} % The style class
\usepackage[bottom=0.5in,right=0.5in,left=0.5in, top=0.5in]{geometry}
\usepackage{hyperref}
\name{Aaron Steinberg}
\address{116 Van Ness Ave, Santa Cruz, California 95060}

\address{+1 (818) 800-2989 $\mid$ aaron@aa.codes $\mid$ azsteinb@ucsc.edu}

\address{\href{https://aa.codes}{https://aa.codes}}

\begin{document}

\begin{rSection}{Education}
    {\bf{University of California, Santa Cruz}}
    \hfill{\em Sept. 2019 - Jun. 2023}
    \\ Bachelor of Computer Science \hfill{ Graduating Jun. 2023 }
\end{rSection}

\begin{rSection}{Work Experience}
    {\bf{Software Engineer Consultant} @  Something Inc.}
    \hfill{\em Apr. 2023}
    \\ API Development with Node.js/Express and Wordpress Plugin Development using PHP

    {\bf{Google Apps Subject Matter Expert} @ UCSC ITS }
    \hfill{\em Dec. 2021 - Present}
    \\ API Development with Node.js/Express based on Google APIs, Technical Writing, and Support.

    {\bf{Bioinformatics Software Engineer Intern} @ Progenabiome}
    \hfill{\em Jul. 2022}
    \\Pipeline development and lab output parsing and analysis using Python and Pandas.


    {\bf{Computer Systems and C Programming Grader} @ UCSC}
    \hfill{\em Mar. 2021 - Jun. 2021}
    \\ Graded projects and papers of 250 students. Helped create automatic grading scripts that tested student code and interacted with the Canvas API to upload grades.

    {\bf{Help Desk Technician} @ UCSC ITS}
    \hfill{\em Dec. 2020 - Dec. 2021}
    \\ Offered technical support for University products to staff, students, and applicants.

    {\bf{Bioinformatics Software Engineer Intern} @ Progenabiome}
    \hfill{\em Jun. 2019 - Sept. 2019}
    \\ Researching and development of stool microbiome and gut flora studies. Lab equipment output parsing using Python and Pandas.
\end{rSection}

\begin{rSection}{Projects and Papers}
    {\bf{AI Journalism:}} An API that writes real news articles about any subject. \href{https://github.com/azsteinb/AIJournalism}{View Project}
    \\{\bf{Locally Imagined:}} An online art market place specialized to Santa Cruz, CA. \href{https://locallyimagined.com/}{View Project}
    \\{\bf{MediBill:}} Medical Bill Analyzer, CruzHacks 2022 First Place Winner. \href{https://devpost.com/software/health-hacker-7soucr}{View Project}
    \\{\bf{A Brief Survey of Data Placement in a Geo-Distributed Storage System using ML}: } \href{https://docs.google.com/document/u/1/d/e/2PACX-1vRi_JSl3urSJMr-Mj7rZGkyrPzMANauaqdgXekPwFfHyUSlrkR0azLyoCxT_S0u2tvndypQ5d6vsJwy/pub}{View Paper}
    \\{\bf{Reverse Proxy Load Balancer:} } Written entirely in C. Available upon request, please send me an email.
    \\{\bf{More Projects:} } More projects are available to see on my GitHub: \href{https://github.com/azsteinb}{View my GitHub.}
\end{rSection}

\begin{rSection}{Skills}
    {\bf{Programming Languages:} } C, C++, C\#, GO, Haskell, Java, Javascript, Python, PHP, SQL

    {\bf{Technologies, Libraries, Frameworks:} } Node.js, Express, React, jQuery, GOA, Postgresql, OpenAPI, GraphQL, Heroku, Amazon S3, Google Cloud, Unix/Linux, Git, WordPress

    {\bf{Other Skills:} } SCRUM, Teamwork, Leadership, Public Speaking, Software Testing, Technical Writing, Documentation, Creative Writing, Teaching, Mountain Biking
\end{rSection}

\begin{rSection}{Relevant Course Work}
    {\bf{Computer Science and Mathematics:} } Cryptography, Analysis of Algorithms, Computational Models, Distributed Systems, Full Stack Web Development,
    Software Engineering, Natural Language Processing, Applied Machine Learning, Functional Programming, Principals of Computer System Design, Computer Architecture, Data Structures \& Algorithms,
    Computer Systems \& C Programming, Computer Systems \& Assembly Language, Programming Abstractions, Networking, Historical Mathematics, Probability and Statistics, Applied Discrete Mathematics, Linear Algebra, Vector Calculus
\end{rSection}
    

\end{document}